%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

% Originally was 10.999999999999pt, as information gets more extensive, get closer to this value %
\documentclass[letterpaper,11.000000001 pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\urlstyle{same}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeEducationEntry}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \\
      \textit{\small#2} & \textit{\small #3} \hfill
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSingleLineSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small#2} \\
    \end{tabular*}\vspace{-6pt}
}



\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape \underline{Aspen Johnson}} \\ \vspace{5pt}
    \small +1 (561) 299-8424 $|$ \href{mailto:aspenjohnson2024@gmail.com}{aspenjohnson2024@gmail.com} $|$
    \href{https://www.linkedin.com/in/aspenjjohnson/}{linkedin.com/in/aspenjjohnson/} $|$
    \href{https://github.com/DormantBillionaire}{github.com/DormantBillionaire} $|$
    \href{https://www.aspenhq.dev/}{www.aspenhq.dev}
\end{center}

%-----------EDUCATION-----------

\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationEntry
      {Valdosta State University}
      {B.S in Data Science: Computational Sci. \& Eng. Track, Minors in Physics and Math}
      {Expected: 2027, GPA: N/A}

    \resumeEducationEntry
      {Palm Beach State College}
      {A.A in STEM: Mechanical/ Aerospace Engineering Track}
      {Expected: Summer 2026, GPA: 3.5}
  \resumeSubHeadingListEnd
  
%-----------PUBLICATIONS-----------
\section{Publications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://www.tandfonline.com/doi/full/10.1080/13504851.2025.2606928}{\textbf{An empirical application of improved gradient scaling for score-driven volatility filters}}}{Mercer University}
      \resumeItem{ - Selected as 1 of 15 research papers to present a lecture at the 2026 Atlanta Research Conference.}
      \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Research Experience}
% LONG MEMORY SEISMICITY RESEARCH WITH SZABI %
  \resumeSubHeadingListStart  
    \resumeSubheading
      {Research Assistant $|$ Long-Memory Time Series \& Seismicity Modelling}{June 2026 – Present}
      {Faculty Guided Research w/  \href{https://business.mercer.edu/faculty-and-insights/faculty-directory/dr-szabolcs-blazsek/}{Prof. Szabolcs Blaszek}}{Remote}
      \resumeItemListStart
        \resumeItem{Studied long-memory dynamics, persistence, and fractional integration as tools for analyzing complex real-world systems in Alaska and California.}
        \resumeItem{Explored public earthquake datasets from sources such as USGS and NOAA to evaluate how seismic activity can be transformed into interpretable time-series variables.}
        \resumeItem{Analyzed over 50 years of earthquake data, totaling more than 2 million data points, collected through a custom Python web-scraping script using USGS database queries.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% PARTICLE ILLIQUIDITY RESEARCH WITH MUBIN %
\resumeSubHeadingListStart  
    \resumeSubheading
      {Computational Physics Researcher $|$ Atomic Particle Simulation \& Modeling}{April 2026 – Present}
      {Faculty Guided Research w/ \href{https://www.valdosta.edu/about/directory/profile/smubin}{Prof. Shafat Mubin}}{On-Site/Remote}
      \resumeItemListStart
      \resumeItem{Studied the Velocity Autocorrelation Function (VACF) to analyze how particle velocities evolve over time in molecular dynamics trajectories.}
      \resumeItem{Investigated how velocity data can be modeled using Gaussian distributions to better understand equilibrium behavior in simulated systems.}  
      \resumeItem{Developed foundational knowledge in molecular dynamics, time-series behavior, and simulation-based scientific computing.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {Financial Econometrics Researcher $|$ Score-driven Voltaility Filters}{Jan 2025 – Dec 2025}
      {Faculty Guided Research w/ \href{https://business.mercer.edu/faculty-and-insights/faculty-directory/dr-szabolcs-blazsek/}{Prof. Szabolcs Blaszek} and \href{https://www.linkedin.com/in/adamkobor/}{Adam Kobor}}{On-Site/Remote}
      \resumeItemListStart
      \resumeItem{Contributed to work showing that Hessian-driven gradient scaling can improve volatility-filter performance relative to existing scaling methods.}
      \resumeItem{Gained publication experience through faculty-guided research involving model interpretation, literature review, empirical analysis, and manuscript development.}
        \resumeItem{Analyzed financial time-series data across Bitcoin, S\&P 500, Gold, U.S. REITs, and CHF/JPY from 2010--2025 using R, GAUSS, Excel, and Bloomberg Terminal data.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart  
    \resumeSubheading
      {Financial Analyst Intern}{May 2025 – Dec 2025}
      {\href{https://www.zinzino.com/site/us/en-us/}{Zinzino USA}}{Remote}
      \resumeItemListStart
        \resumeItem{Reduced chargeback processing time by 87\% through workflow digitization and documentation streamlining.}
        \resumeItem{Refined the charge back process within a few weeks of arrival, and curated a reference guide to aid future onboarding employees.}
        \resumeItem{Created clear documentation that enabled cross-departmental collaboration and made Finance operations easy for shareholders and upline leaders to understand.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------LEADERSHIP, ATHLETICS, AND SERVICE -----------
\section{Leadership, Athletics, and Service}
% LONG MEMORY SEISMICITY RESEARCH WITH SZABI %
  \resumeSubHeadingListStart  
    \resumeSubheading
      {Collegiate Women's Basketball Player}{June 2022 -- Present}
      {Mercer University $|$ Valdosta State University}{NCAA Division I $|$ Division II}
      \resumeItemListStart
        \resumeItem{Commit 20--25+ hours per week to practices, strength training, film study, travel, competition, recovery, and team responsibilities while balancing full-time academic and research commitments.}
        \resumeItem{Develop leadership, discipline, time management, communication, resilience, and performance under pressure through year-round collegiate athletics.}
        \resumeItem{Represent university athletic programs in competitive, team-based environments requiring accountability, preparation, adaptability, and consistent execution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------AI/ML + Physics PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\href{https://github.com/DormantBillionaire/cc-me-planner}{\textbf{CC-Me-Planner}} $|$ \emph{HTML, CSS, and JS}}{\textbf{(In Progress)}}
          \resumeItemListStart
            \resumeItem{Developing a full-stack academic planning web application designed to simplify semester, AA, and bachelor's degree scheduling for community college students.}
            \resumeItem{Designing with accessibility at the forefront, addressing barriers faced by returning adults, first-generation students, and transfer-track students.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{CourtSignal} $|$ \emph{Assistive Technology for Hearing Impaired Athletes}}{\textbf{(In Progress)}}
          \resumeItemListStart
            \resumeItem{Developing an assistive technology concept designed to improve real-time communication access for deaf and hard-of-hearing athletes in competitive sports environments.}
            \resumeItem{Selected for the University System of Georgia and Georgia Tech's inaugural 2026 Startup Studio seminar to advance the project through entrepreneurship training, customer discovery, and early-stage product validation.}
            \resumeItem{Researching communication barriers faced by athletes with hearing loss, including coach instruction, teammate coordination, and environmental awareness during practices and games.}
            \resumeItem{Exploring software-based design approaches that prioritize accessibility, mobility, and practical use within high-performance athletic settings.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

    

%-----------EXTRACURRICULAR ACTIVITIES-----------
\section{Leadership, Community Engagement \& Extracurriculars}
  \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Read2Succeed} $|$ \emph{Tutoring elementary students to aid in building literary in Macon, Georgia}}{}
        \resumeProjectHeading
          {\href{https://maa.org/putnam/}{\textbf{Putnam Mathematics Competition Prep}} $|$ \emph{Independent Study}}{}
        \resumeProjectHeading
          {\href{https://www.lifesportsacademy.net/home}{\textbf{Youth Sports Volunteer}} $|$ \emph{Assisted young athletes K-12 in a variety of sports. }}{}
        \resumeProjectHeading
          {\href{https://www.meetup.com/physicswithfriends/}{\textbf{Weekly Physics Study Group Member}} $|$ \emph{Going through \textbf{Helliwell's Modern Classical Mechanics} text}}{}
        \resumeProjectHeading
          {\textbf{\href{https://csel.mercer.edu/student-engagement/book-clubs/}{Book Club Fellow}} $|$ \emph{Selected as one of ten students to participate through Mercer Universities Economics Department}}{}
        \resumeProjectHeading
          {\textbf{\href{https://www.youtube.com/@AP4Pres}{Content Creation}} $|$ \emph{Streamed myself doing psets and projects on youtube amassing $\sim$20,000 views}}{}
        \resumeProjectHeading
          {\textbf{\href{https://www.gotostage.com/channel/ae3be1897f1e486ebe5a0a0d417396e2/recording/6ecf53ff64484050af20f49c86a9d760/watch}{AWS Campus Prep Series Participant}} $|$ \emph{Completed a Summer-long series of webinars regarding Amazon Careers and Cloud Services}}{}
  \resumeSubHeadingListEnd

%
%-----------SKILLS & OTHER-----------
\begin{minipage}[t]{0.48\textwidth}
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages in order of proficiency}{: Python, Java, LaTeX, \newline HTML/CSS, R, Gauss, C/C++, JavaScript, Octave} \\
     \textbf{Developer Tools}{: Git, CLI, VSCode} 
    }}
 \end{itemize}
\end{minipage}
\hfill
\vrule
\hfill
\begin{minipage}[t]{0.48\textwidth}
\section{Other}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Clubs/Organizations}{:NSBE, SWE, and \newline Codecademy's Women in Tech} \\
    }}
 \end{itemize}
\end{minipage}
%-------------------------------------------
\end{document}
