%-------------------------
% Resume in Latex
% Author : Aspen Johnson
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

\urlstyle{same}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.1pt}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeEducationEntry}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \\
      \textit{\small#2} & \textit{\small #3} \hfill
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape \underline{Aspen Johnson}} \\ \vspace{5pt}
    \small +1 (561) 299-8424 $|$ \href{mailto:aspenjohnson2024@gmail.com}{aspenjohnson2024@gmail.com} $|$
    \href{https://www.linkedin.com/in/aspenjjohnson/}{linkedin.com/in/aspenjjohnson/} $|$
    \href{https://github.com/DormantBillionaire}{github.com/DormantBillionaire} $|$
    \href{https://www.aspenhq.dev/}{www.aspenhq.dev}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationEntry
      {Valdosta State University}
      {Incoming B.S. in Data Science: Computational Science \& Engineering Track; Minors: Physics and Mathematics}
      {}

    \resumeEducationEntry
      {Palm Beach State College}
      {A.A. in STEM: Mechanical \& Aerospace Engineering Track}
      {Completed May 2026, GPA: 3.20}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
        
    \resumeSubheading
      {Collegiate Women's Basketball Player}{June 2022 -- Present}
      {Mercer University; Valdosta State University}{NCAA Division I / Division II}
      \resumeItemListStart
        \resumeItem{Commit 20--25+ hours per week to practices, strength training, film study, travel, competition, recovery, and team responsibilities while balancing full-time academic and research commitments.}
        \resumeItem{Develop leadership, discipline, time management, communication, resilience, and performance under pressure through year-round collegiate athletics.}
        \resumeItem{Represent university athletic programs in competitive, team-based environments requiring accountability, preparation, adaptability, and consistent execution.}
      \resumeItemListEnd

    \resumeSubheading
      {Physics Undergraduate Researcher}{Mar 2026 -- Present}
      {Valdosta State University}{On-Site/Remote}
      \resumeItemListStart
        \resumeItem{Studied the Velocity Autocorrelation Function to analyze how particle velocities evolve over time in molecular dynamics trajectories.}
        \resumeItem{Investigated how velocity data can be modeled using Gaussian distributions to better understand equilibrium behavior in simulated systems.}
        \resumeItem{Review model outputs, visualizations, and research notes for accuracy, clarity, reproducibility, and consistency before faculty discussion.}
      \resumeItemListEnd

    \resumeSubheading
      {Econometrics Undergraduate Researcher}{Jan 2025 -- Dec 2025}
      {Mercer University}{On-Site/Remote}
      \resumeItemListStart
        \resumeItem{Co-authored \href{https://www.tandfonline.com/doi/full/10.1080/13504851.2025.2606928}{\textit{An empirical application of improved gradient scaling for score-driven volatility filters}}, published in \textit{Applied Economics Letters}, Taylor \& Francis, 2025.}
        \resumeItem{Contributed to data curation, formal analysis, methodology, software implementation, validation, visualization, and manuscript preparation for empirical testing of the Hessian-filter scaled Beta-t-EGARCH volatility model.}
        \resumeItem{Analyzed financial time-series data across Bitcoin, S\&P 500, Gold, U.S. REITs, and CHF/JPY from 2010--2025 using R, GAUSS, Excel, and Bloomberg Terminal data.}
        \resumeItem{Selected as 1 of 15 research papers to present a lecture at the 2026 Atlanta Research Conference.}
      \resumeItemListEnd

    \resumeSubheading
      {Financial Analyst Intern}{May 2025 -- Dec 2025}
      {\href{https://www.zinzino.com/site/us/en-us/}{Zinzino USA}}{Remote}
      \resumeItemListStart
        \resumeItem{Reduced chargeback processing time by 87\% through workflow digitization, documentation streamlining, and process-improvement analysis.}
        \resumeItem{Created reference documentation to support onboarding, data quality, process consistency, and cross-functional accuracy.}
        \resumeItem{Reviewed finance-related documentation and case details for completeness, accuracy, and clarity before sharing guidance with internal stakeholders.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Econometric Modeling in Complex Physical Systems} $|$ \emph{Python, R, Time-Series Analysis, Volatility Modeling}}{}
      \resumeItemListStart
        \resumeItem{Investigating whether GARCH-family and long-memory time-series models can be adapted to complex physical systems exhibiting clustering, persistence, uncertainty, or volatility-like behavior.}
        \resumeItem{Sourcing and structuring geophysical datasets from USGS, NOAA, and NCAR, including seismic activity, geomagnetic storms, and solar wind turbulence, for empirical model validation.}
        \resumeItem{Exploring how financial-market modeling tools may support broader analysis of event clustering, infrastructure-adjacent risk, system behavior, and reliability-focused interpretation.}
        \resumeItem{Documenting model assumptions, limitations, data quality issues, and interpretation risks to support reproducible research workflows and avoid overclaiming predictive results.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Assistive Hearing Technology Concept} $|$ \emph{Accessibility Research, Signal Processing, Embedded Systems}}{}
      \resumeItemListStart
        \resumeItem{Investigating a low-cost assistive hearing technology concept combining accessibility research, audio/signal processing concepts, embedded systems, and human-centered design.}
        \resumeItem{Researching how microphones, sensors, microcontrollers, and software-based filtering could support improved sound awareness in athletic events and high-noise environments.}
        \resumeItem{Documenting user needs, technical requirements, component options, and design constraints for future prototype development and applied technology testing.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{DIY Cyberdeck / Portable Computing Hardware System} $|$ \emph{Fusion 360, KiCad, PCB Design, Embedded Systems}}{}
      \resumeItemListStart
        \resumeItem{Designing a modular portable computing device inspired by the \href{https://www.clockworkpi.com/home-uconsole}{ClockworkPi uConsole}, emphasizing enclosure constraints, component layout, usability, repairability, and field-ready portability.}
        \resumeItem{Using Fusion 360 to prototype enclosure concepts, internal spacing, mounting points, and component placement for a compact hardware system.}
        \resumeItem{Learning KiCad workflows for schematic capture, PCB layout, component selection, and hardware design documentation.}
        \resumeItem{Applying electronics, electromagnetism, embedded systems, and hardware/software integration concepts to strengthen applied engineering and technical documentation skills.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership, Community Engagement \& Extracurriculars}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\href{https://www.meetup.com/physicswithfriends/}{\textbf{Weekly Physics Study Group Member}} $|$ \emph{Studying Helliwell's \textit{Modern Classical Mechanics}}}{}

    \resumeProjectHeading
      {\textbf{Read2Succeed Tutor} $|$ \emph{Supported elementary literacy development and student confidence at Matilda Hartley Elementary}}{}

    \resumeProjectHeading
      {\textbf{AWS Campus Prep Series Participant} $|$ \emph{Completed career and cloud-focused webinar series}}{}

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
{\small
\textbf{Programming \& Analysis:} Python, R, GAUSS, Java, C/C++, JavaScript, Octave, Excel \\

\textbf{Data Science \& Modeling:} Data cleaning, exploratory data analysis, time-series analysis, statistical modeling, model validation, data visualization, forecasting concepts \\

\textbf{AI/Data Review:} AI response evaluation, prompt testing, data annotation, data labeling, data quality review, pattern recognition \\

\textbf{Engineering \& Prototyping:} Fusion 360, KiCad, PCB design fundamentals, circuit design fundamentals, embedded systems concepts, technical diagrams \\

\textbf{Tools:} NumPy, Matplotlib, Seaborn, Google Colab, \LaTeX, Git, CLI, VS Code, Bloomberg Terminal \\

\textbf{Research \& Documentation:} Literature review, technical writing, reproducible notes, model comparison, workflow documentation
}
%-------------------------------------------
\end{document}